CF Nutrition Pre- and Post-CFTR Modulator

### 2022-09-23 Edith Zemanick/CF Nutrition/cf_nutrition.qmd
liver labs mostly done

```{r}
# Import all data
df = read.csv("/Users/timvigers/Documents/Work/Vigers/CF/Edith Zemanick/CF Nutrition/Data_Cleaned/analysis.csv")
df$Timepoint = factor(df$Timepoint,levels = c("Pre","Post"))
```

@@

```{r}
t1 = tableby(First.Modulator~Vitamin.A+Vitamin.D+Vitamin.E.Alpha+
           ppFEV1+BMI.Percentile+ALT+AST+GGTP,data = df[df$Timepoint == "Pre",])
summary(t1,pfootnote = T)
```

@@

```{r results='asis'}
p = paired(Timepoint~Vitamin.A+Vitamin.D+Vitamin.E.Alpha+
           ppFEV1+BMI.Percentile+ALT+AST+GGTP,data = df,id=ID,control = list(numeric.test = "signed.rank"))
summary(p,pfootnote = T)
```

>>>>

```{r}
# Import all data
df = read.csv("/Users/timvigers/Documents/Work/Vigers/CF/Edith Zemanick/CF Nutrition/Data_Cleaned/analysis.csv",na.strings = "",check.names = F)
df$Timepoint = factor(df$Timepoint,levels = c("Pre","Post"))
```

@@

```{r results='asis'}
t1 <- tableby(`First Modulator` ~ `Vitamin A` + `Vitamin D` + `Vitamin E Alpha` +
  `ppFEV1` + `BMI Percentile` +
  `ALT` + `High ALT (3x)` + `High ALT (5x)` +
  `AST` + `High AST (3x)` + `High AST (5x)` +
  `GGTP` + `High GGTP (3x)` + `High GGTP (5x)`,
data = df[df$Timepoint == "Pre", ]
)
summary(t1, pfootnote = T)
```

@@

```{r results='asis'}
p <- paired(Timepoint ~ `Vitamin A` + signed.rank(`Vitamin D`) + `Vitamin E Alpha` +
  `ppFEV1` + `BMI Percentile` +
  signed.rank(`ALT`) + `High ALT (3x)` + notest(`High ALT (5x)`) +
  signed.rank(`AST`) + `High AST (3x)` + notest(`High AST (5x)`) +
  signed.rank(`GGTP`) + notest(`High GGTP (3x)`) + notest(`High GGTP (5x)`),
data = df, id = ID
)
summary(p, pfootnote = T)
```
